### 2019-08-14 paper_04_shallow_water/Latex/article.tex
Formatting equations
Proof read swe paper

% \begin{abstract}
%
% The dynamics of irrotational shallow water wave turbulence forced in large
% scales and dissipated at small scales is investigated. First, we derive the
% shallow water analogue of the `four-fifths law' of Kolmogorov turbulence
% for a third order structure function involving velocity and displacement
% increments. Using this relation and assuming that the flow is dominated by
% shocks we develop a simple model predicting that the shock amplitude scales as
% $ (\epsilon d)^{1/3} $, where $ \epsilon $ is the mean dissipation rate and $ d $
% the mean distance between the shocks, and that the $ p $:th order displacement
% and velocity structure functions scale as $ (\epsilon d)^{p/3} r/d $, where $ r $
% is the separation. Then we carry out a series of forced simulations with
% resolutions up to $7680^2$, varying the Froude number, $F_{f} = (\epsilon L_f)^{1/3}/
% c $, where $ L_f $ is the forcing length scale  and $c$ is the wave
% speed. In all simulations a stationary state is reached in which there is a
% constant spectral energy flux and equipartition between kinetic and potential
% energy in the constant flux range. The third order structure function relation
% is satisfied with a high degree of accuracy. Mean energy is found to scale approximately as $
% E \sim \sqrt{\epsilon  L_f  c} $, and is also dependent on resolution, indicating
% that shallow water wave turbulence does not fit into the paradigm of a
% Richardson-Kolmogorov cascade. In all simulations shocks develop, displayed as
% long thin bands of negative divergence in flow visualisations. The mean
% distance between the shocks is found to scale as $ d \sim F_f^{1/2} L_f $.
% Structure functions of second and higher order are found to scale in good
% agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow
% 0 $, shocks will become denser and weaker and finally disappear for a finite
% Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small,
% shocks will prevail if the Reynolds number is sufficiently large.
%
% \end{abstract}
%
% \begin{keywords}
% \end{keywords}

@@

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single layer SW equations are very quite to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wave number.
%

%
Due to their relative simplicity, the SW equations have
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}. Balanced flows have a dynamics which is very similar to
two-dimensional turbulence, with an upscale energy cascade. %
Small scale energy dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989}.   \cite{YuanHamilton1994} showed that
statistically stationary shallow-water flows can be obtained by forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales. They suggested that the $ k^{-5/3} $ energy spectrum observed at   atmospheric mesoscales  \cite[]{NastromGage1985,LiLindborg2018} is generated by a downscale cascade of gravity waves which may be captured by the SW equations.

The $ k^{-5/3} $ spectrum has been reproduced 
 by some General Circulation Models (GCM:s) based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008}.  \cite{AugierLindborg2013}  formulated a spectral energy budget of kinetic and available potential energy in terms of spherical harmonics and used this formulation to investigated two GCM:s. It was found that one of the models -- named the AFES model -- was able to reproduce a downscale energy cascade with realistic $ k^{-5/3} $ mesoscale spectra. The result was almost too good, since the AFES model simulation only contained 21 vertical levels, while theoretical arguments based on stratified turbulence theory \cite[]{Lindborg2006} suggest that a much finer vertical resolution would be needed. This lead us to ask what number of vertical levels a model needs in order  to reproduce a downscale energy cascade. Was \cite{YuanHamilton1994}  right  when they suggested that even a single layer model, such as the SW equations, could do the job? 
The original motivation of this study was to investigate this suggestion. A first set of
simulations of the SW equations, containing both balanced and gravity wave motions,
showed some encouraging results. Indeed, gravity waves were transferring energy towards
small scales. However, after a while it became clear that the cascade was not as strong
as in the GCM simulation.  Moreover, in all the SW simulations we observed shocks with
an associated $ k^{-2} $-spectrum rather than a $ k^{-5/3} $-spectrum. These
observations lead us to dismiss the SW equations as a model for the atmospheric
downscale cascade. Based on the SW equations we developed another two-dimensional toy
model  \cite[]{LindborgMohanan2017} that is absent of shocks and can reproduce the
energy cascade in the GCM quite well, including a $ k^{-5/3}  $-spectrum.

The shocks we observed in the SW simulations left us in a state of curiosity. In some simulations they appeared to be rather strong and in others rather weak. In some simulations they were densely packed and in others sparsely distributed.
In what way  do the input parameters regulate these variations? Will there always be shocks or will they disappear in the limit of weak nonlinearities?  Such questions made us to shift our theoretical focus and pursue the study, despite the fact that the answer to the question that originally motived it turned out to be negative.

Some predictions  based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011} may be of relevance in the limit of weak nonlinearities. In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
solutions of the kinetic equation corresponding to a constant downscale energy
flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
of the form $ E(k) \sim k^{-3/2} $ for three-dimensional acoustic turbulence. This prediction is
of particular interest, since the acoustic equations and the SW equations are similar 
to the equations describing acoustic turbulence. It may be questioned, however, that weak turbulence formalism is
applicable to acoustic and SW wave turbulence, no matter how weak the
nonlinearities are supposed to be.  \cite{KadomtsevPet1973} argued that shocks always will always develop in acoustic turbulence, also in the limit of weak nonlinearities, due to the fact that acoustic waves are nondispersive.

Shocks have been been observed in many simulations of the SW equations \cite[]{FargeSadourny1989,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}. As shown by \cite{Burgers1948} in the one-dimensional case and \cite{Kuznetsov2004} in the two- and three-dimensional cases, the energy spectrum of a flow dominated by
shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
great number of simulations of Burgers equation \cite[for a review, see ]
[]{Frisch2001}. The shocks also lead to very strong intermittency, as
demonstrated by \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced dissipative simulations of the SW equations showing similar spectra.
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation. Clearly, a new study of two-dimensional shock dominated wave turbulence can bring some more light on the problem.

@@

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu   
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite. This can only be accomplished by permitting the term to be nonlinear in the flow variables. There are different forms of nonlinear terms that fulfil both conditions and it may be disputed which is the best one. However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfil any of these two conditions in a strict sense and we will therefore not discuss this matter further. The inviscid SW equations conserve a local
quantity along trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity.  This conservation law will be of no relevance in the present study in which we only consider
irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential. In a domain with no net fluxes through the boundaries the inviscid equations conserve energy, $ E = E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy. The latter can be split into three terms as \begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2, 
\end{equation}
where the first term corresponds to the potential energy of a state with no
surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}. As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
 The velocity potential and the displacement of the linearised inviscid SW equations both satisfy the wave equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between KE and APE over a wave period in each Fourier mode.

In order to analyze the spectral flux of energy, we derive the spectral energy
budget, i.e.\ the governing equations for spectral KE and APE
functions. This is not as straightforward as in incompressible turbulence since
the expression of the kinetic energy  is not
quadratic. To define the spectral KE function, we use the relation
\begin{equation}
\mean { E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
\end{equation}
where
\begin{equation}
\scalarprod{\baa}{\bb} \equiv \Re\{ \hat \baa(\kk)^* \cdot \hat \bb(\kk) \},
\end{equation}
and $\Re$ denotes the real part, $\kk$ is the wave number and the
hat denotes the Fourier transform.
%
The spectral KE function can therefore be defined as
\begin{equation}
E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2.
\end{equation}
Similarly, the APE can be written as the sum over all wave numbers of
the spectral APE function 
\begin{equation}
E_A(\kk) =  c^2 \scalarprod{\eta}{\eta}/2 \, .
\end{equation}
The inviscid equation for the spectral KE and APE functions can be written as
\begin{eqnarray}
\p_t E_K(\kk) &=& T_K(\kk) - C (\kk),\\
\p_t E_A(\kk) &=& T_A(\kk) + C (\kk),
\end{eqnarray}
where
\begin{equation}
T_K(\kk) 
= -\scalarprod{\bnabla \cdot \uu}{E_K} 
-\scalarprod{\uu }{\bnabla E_K } \, ,
\end{equation}
\begin{equation}
T_A(\kk) = -c^2 \scalarprod{\bnabla \eta }{\JJ}- c^2\scalarprod{\eta}{\bnabla \cdot \JJ}  \, ,
\end{equation}
are the spectral transfer functions of KE and APE, respectively, and
\begin{equation}
C (\kk) 
= \scalarprod{\uu}{\bnabla E_P}
\end{equation}
is the spectral KE-APE conversion function.
The spectral energy flux functions of KE and APE are defined as
\begin{eqnarray}
\Pi_K (k) = \sum_{| {\bf k}^{\prime} | > k} T_K ( {\bf k}^\prime ) \, , \;\;\;  \Pi_A (k) = \sum_{| {\bf k}^{\prime} | > k} T_A ( {\bf k}^\prime ) 
\end{eqnarray}

We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third order velocity structure function of incompressible isotropic turbulence.   In the case of irrotational SW wave turbulence the analogous law contains a third order structure function involving both velocity and displacement increments.  In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational. To derive the law it is convenient to start from the following equations
\begin{eqnarray} \label{IRR}
\p_t \uu &=& -\bnabla  (\uu \cdot \uu /2) - c^2 \bnabla h  \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ \, ,
\end{eqnarray}
where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find

>>>>

% \begin{abstract}
%
% The dynamics of irrotational shallow water wave turbulence forced in large
% scales and dissipated at small scales is investigated. First, we derive the
% shallow water analogue of the `four-fifths law' of Kolmogorov turbulence
% for a third order structure function involving velocity and displacement
% increments. Using this relation and assuming that the flow is dominated by
% shocks we develop a simple model predicting that the shock amplitude scales as
% $ (\epsilon d)^{1/3} $, where $ \epsilon $ is the mean dissipation rate and $ d $
% the mean distance between the shocks, and that the $ p $th-order displacement
% and velocity structure functions scale as $ (\epsilon d)^{p/3} r/d $, where $ r $
% is the separation. Then we carry out a series of forced simulations with
% resolutions up to $7680^2$, varying the Froude number, $F_{f} = (\epsilon L_f)^{1/3}/
% c $, where $ L_f $ is the forcing length scale  and $c$ is the wave
% speed. In all simulations a stationary state is reached in which there is a
% constant spectral energy flux and equipartition between kinetic and potential
% energy in the constant flux range. The third order structure function relation
% is satisfied with a high degree of accuracy. Mean energy is found to scale approximately as $
% E \sim \sqrt{\epsilon  L_f  c} $, and is also dependent on resolution, indicating
% that shallow water wave turbulence does not fit into the paradigm of a
% Richardson-Kolmogorov cascade. In all simulations shocks develop, displayed as
% long thin bands of negative divergence in flow visualisations. The mean
% distance between the shocks is found to scale as $ d \sim F_f^{1/2} L_f $.
% Structure functions of second and higher order are found to scale in good
% agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow
% 0 $, shocks will become denser and weaker and finally disappear for a finite
% Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small,
% shocks will prevail if the Reynolds number is sufficiently large.
%
% \end{abstract}
%
% \begin{keywords}
% \end{keywords}

@@

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single-layer SW equations are quite similar to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearised operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wavenumber.
%

%
Due to their relative simplicity, the SW equations have
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}. Balanced flows have a dynamics which is very similar to
two-dimensional turbulence, with an upscale energy cascade. %
Small scale energy dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989}.   \cite{YuanHamilton1994} showed that
statistically stationary shallow water flows can be obtained by forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales. They suggested that the $ k^{-5/3} $ energy spectrum observed at   atmospheric mesoscales  \cite[]{NastromGage1985,LiLindborg2018} is generated by a downscale cascade of gravity waves which may be captured by the SW equations.

The $ k^{-5/3} $ spectrum has been reproduced
 by some General Circulation Models (GCMs) based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008}.  \cite{AugierLindborg2013}  formulated a spectral energy
budget of kinetic and available potential energy in terms of spherical
harmonics and used this formulation to investigated two GCMs. It was found that
one of the models -- named the Atmospheric GCM for the Earth Simulator (AFES)
model -- was able to reproduce a downscale energy cascade with realistic $
k^{-5/3} $ mesoscale spectra. The result was almost too good, since the AFES
model simulation only contained 21 vertical levels, while theoretical arguments
based on stratified turbulence theory \cite[]{Lindborg2006} suggest that a much
finer vertical resolution would be needed. This leads us to ask what number of vertical levels a model needs in order  to reproduce a downscale energy cascade. Was \cite{YuanHamilton1994}  right  when they suggested that even a single-layer model, such as the SW equations, could do the job?
The original motivation for this study was to investigate this suggestion. A first set of
simulations of the SW equations, containing both balanced and gravity wave motions,
showed some encouraging results. Indeed, gravity waves were transferring energy towards
small scales. However, after a while it became clear that the cascade was not as strong
as in the GCM simulation.  Moreover, in all the SW simulations we observed shocks with
an associated $ k^{-2} $-spectrum rather than a $ k^{-5/3} $-spectrum. These
observations lead us to dismiss the SW equations as a model for the atmospheric
downscale cascade. Based on the SW equations we developed another two-dimensional toy
model  \cite[]{LindborgMohanan2017} that is absent of shocks and can reproduce the
energy cascade in the GCM quite well, including a $ k^{-5/3}  $-spectrum.

The shocks we observed in the SW simulations left us in a state of curiosity. In some simulations they appeared to be rather strong and in others rather weak. In some simulations they were densely packed and in others sparsely distributed.
In what way  do the input parameters regulate these variations? Will there
always be shocks or will they disappear in the limit of weak nonlinearities?
Such questions made us to shift our theoretical focus and pursue this question, despite the fact that the answer to the question that originally motived it turned out to be negative.

Some predictions  based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011} may be of relevance in the limit of weak nonlinearities. In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
solutions of the kinetic equation corresponding to a constant downscale energy
flux are associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
\cite{ZakharovSagdeev1970} used the weak turbulence formalism to derive a spectrum
of the form $ E(k) \sim k^{-3/2} $ for three-dimensional acoustic turbulence. This prediction is
of particular interest, since the acoustic equations and the SW equations are similar
to the equations describing acoustic turbulence. However, it is questionable that
the weak turbulence formalism is
applicable to acoustic and SW wave turbulence, no matter how weak the
nonlinearities are supposed to be.  \cite{KadomtsevPet1973} argued that shocks always will always develop in acoustic turbulence, also in the limit of weak nonlinearities, due to the fact that acoustic waves are non-dispersive.

Shocks have been observed in many simulations of the SW equations \cite[]{FargeSadourny1989,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}. As shown by \cite{Burgers1948} in the one-dimensional case and \cite{Kuznetsov2004} in the two- and three-dimensional cases, the energy spectrum of a flow dominated by
shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
great number of simulations of the Burgers equation \cite[for a review, see ]
[]{Frisch2001}. The shocks also lead to very strong intermittency, as
demonstrated by \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced-dissipative simulations of the SW equations showing similar spectra.
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation. Clearly, a new study of two-dimensional shock dominated wave turbulence can bring some more light on the problem.

@@

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement,
$\nu$ the kinematic viscosity and $ c $ the gravity wave speed. The SW
equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a
matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a
way that momentum is conserved and energy dissipation is positive definite.
This can only be accomplished by permitting the term to be nonlinear in the
flow variables. There are different forms of nonlinear terms that fulfil both
conditions and it may be disputed which is the best one. However, in the
simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq})
that will not fulfil either of these two conditions in a strict sense and we
will therefore not discuss this matter further. The inviscid SW equations
conserve a local
quantity along trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity.  This conservation law will be of no relevance in the present study in which we only consider
irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential. In a domain with no net fluxes through the boundaries the inviscid equations conserve energy, $ E = E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy. The latter can be split into three terms as \begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2,
\end{equation}
where the first term corresponds to the potential energy of a state with no
surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}. As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
 The velocity potential and the displacement of the linearised inviscid SW equations both satisfy the wave equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between kinetic energy (KE) and APE over a wave period in each Fourier mode.

In order to analyse the spectral flux of energy, we derive the spectral energy
budget, i.e.\ the governing equations for spectral KE and APE
functions. This is not as straightforward as in incompressible turbulence since
the expression of the kinetic energy  is not
quadratic. To define the spectral KE function, we use the relation
\begin{equation}
\mean { E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
\end{equation}
where
\begin{equation}
\scalarprod{\baa}{\bb} \equiv \Re\{ \hat \baa(\kk)^* \cdot \hat \bb(\kk) \},
\end{equation}
and $\Re$ denotes the real part, $\kk$ is the wavenumber and the
hat denotes the Fourier transform.
%
The spectral KE function can therefore be defined as
\begin{equation}
E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2.
\end{equation}
Similarly, the APE can be written as the sum over all wavenumbers of
the spectral APE function
\begin{equation}
E_A(\kk) =  c^2 \scalarprod{\eta}{\eta}/2 \, .
\end{equation}
The inviscid equation for the spectral KE and APE functions can be written as
\begin{eqnarray}
\p_t E_K(\kk) &=& T_K(\kk) - C (\kk),\\
\p_t E_A(\kk) &=& T_A(\kk) + C (\kk),
\end{eqnarray}
where
\begin{equation}
T_K(\kk)
= -\scalarprod{\bnabla \cdot \uu}{E_K}
-\scalarprod{\uu }{\bnabla E_K } \, ,
\end{equation}
\begin{equation}
T_A(\kk) = -c^2 \scalarprod{\bnabla \eta }{\JJ}- c^2\scalarprod{\eta}{\bnabla \cdot \JJ}  \, ,
\end{equation}
are the spectral transfer functions of KE and APE, respectively, and
\begin{equation}
C (\kk)
= \scalarprod{\uu}{\bnabla E_P}
\end{equation}
is the spectral KE-APE conversion function.
The spectral energy flux functions of KE and APE are defined as
\begin{eqnarray}
\Pi_K (k) = \sum_{| {\bf k}^{\prime} | > k} T_K ( {\bf k}^\prime ) \, , \;\;\;  \Pi_A (k) = \sum_{| {\bf k}^{\prime} | > k} T_A ( {\bf k}^\prime )
\end{eqnarray}

We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third-order velocity structure function of incompressible isotropic turbulence.   In the case of irrotational SW wave turbulence the analogous law contains a third-order structure function involving both velocity and displacement increments.  In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational. To derive the law it is convenient to start from the following equations
\begin{eqnarray} \label{IRR}
\p_t \uu &=& -\bnabla  (\uu \cdot \uu /2) - c^2 \bnabla h  \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ \, ,
\end{eqnarray}
where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find

\begin{equation}
\p_t ( J_i' u_i ) = - \p_i( J_i'|\uu|^2/2) - \p_i'(u_j J_j' u_i')
-\p_i (J_i' c^2 h)  - \p_i' (u_i E_p')
\end{equation}
and
\begin{equation}
\p_t ( h' h ) = - \p_i( h'J_i ) - \p_i'( hJ_i' ),
\end{equation}
which gives
\begin{flalign}
&\p_t ( \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h ) \nonumber\\
&= - \p_i( J_i'|\uu|^2/2) - \p_i'( J_i|\uu'|^2/2) %\nonumber \\&&
   - \p_i'(u_j J_j' u_i') - \p_i(u_j' J_j u_i) %\nonumber\\
   -c^2\p_i (J_i'h) \nonumber\\
&\quad- c^2\p_i' (J_ih') - \p_i' (u_i E_p') - \p_i (u_i' E_p) %\nonumber\\
 -2c^2\p_i' (J_i'h) - 2c^2\p_i (J_ih').
\end{flalign}
We then assume homogeneity and take the average denoted by
$\meane{}$.   For
every function $g(\xx, \xx')$, we have $\p_i' \meane{g} =
-\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We thus obtain
\begin{eqnarray}
\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
&=& + \bnabla_{\rr}\cdot\meane{ \JJ'|\uu|^2/2 - \JJ|\uu'|^2/2 } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ u_j J_j' \uu' - u_j' J_j \uu } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ \uu E_p'- \uu' E_p } \nonumber\\
&& -c^2\bnabla_{\rr}\cdot\meane{ \JJ'h - \JJ h' }
\end{eqnarray}
%
We then introduce the structure functions and the operator $\delta$
returning the increment of a variable between two points separated by $\rr$,
for example $\delta h (\xx, \rr) = h(\xx+\rr)- h(\xx)$.
%
Using homogeneity again, we obtain
\begin{equation}
\meane{ (\delta h)^2 \delta\uu } =
-\meane{ h'^2 \uu } + \meane{ h^2 \uu' }
+2\meane{ hh' \uu } - 2\meane{ hh' \uu' }
\end{equation}
and
\begin{equation}
\meane{ |\delta \uu|^2 \delta\JJ } =
\meane{  |\uu|^2 \JJ' } - \meane{ |\uu'|^2\JJ }
+\meane{ u_ju_j' \JJ' } - \meane{  u_ju_j' \JJ },
\end{equation}
which gives
\begin{equation} \label{FluxT}
2\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
= \bnabla_{\rr} \cdot ( \meane{ |\delta \uu|^2 \delta\JJ }
+ c^2\meane{ (\delta h)^2 \delta\uu } ).
\end{equation}
For separations that are considerably larger than dissipative scales of motion and considerably smaller than forcing scales a standard argument \cite[see for example][]{Frisch} gives that the left-hand side is approximately equal to $ -8 \epsilon $, where $ \epsilon $ is the mean dissipation rate. It is interesting to note that a factor of $ 8 $ appears in the case when the velocity field is irrotational while a corresponding factor of $ 4 $ appears in the case when the velocity field is non-divergent.
Assuming isotropy and integrating yield the Kolmogorov law for
irrotational shallow water wave  turbulence
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L }
+ c^2\meane{ (\delta h)^2 \delta u_L } = -4 \epsilon r, \label{eq_Kolmo}
\end{equation}
where $J_L \equiv
\JJ\cdot\rr / |\rr|$ and $u_L \equiv \uu\cdot\rr / |\rr|$ are
longitudinal increments.

We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
Our analysis has some similarities with the analyses by \cite{BouchaudMezardParisi1995}, \cite{WeinanKhaninMazelSinai1997} and \cite{Weinan}
for Burgers equation.
We consider a domain with total area  $ {\mA} $ occupied by shocks which we
consider as smooth lines. We denote the total length of all shocks by $ L_s $.  The mean distance between the shocks within the domain can be estimated as
\begin{equation}
d \simeq \frac{\mA} {L_s} .
\end{equation}
A structure function of a flow variable is defined as the area average of increments  between two points separated by a distance $ r $.
Assuming that the contribution from increments where the two points are not separated by a shock is negligible for higher-order structure functions we obtain
\begin{eqnarray}
\meane{|\delta h|^p}
=  \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p
 \simeq  \frac{r}{\mA} \int_\shocks ds |\cos\theta| |\Delta h (s)|^p,
\end{eqnarray}
where $\theta$ is the angle between the shock normal unit vector and the separation
vector $\rr$ %
and $\Delta h (s)$ is the shock displacement amplitude.
%
Assuming isotropy, the integral can be split and we get
\begin{equation} \label{StepH}
\meane{|\delta h|^p}
\simeq
r \frac{L_s}{\mA} \meant{|\cos\theta|} \means{|\Delta h |^p}
\simeq  \frac{2}{\pi} \means{|\Delta h |^p} \frac{r}{d} ,
\end{equation}
where $\meant{}$ is the mean over $\theta$
and $\means{}$ is the mean over all shocks.
